Exploring Suicide Rates: Assessing Age, Sex and Race Patterns with Statistical Insights into Suicide Risk

### 2024-04-22 paper/paper.qmd
update paper/paper.qmd

This paper presents a comphrehensive statistical model of the relationship between demographic factors - age, sex, and race - and their impact on suicide rates. Our objective is to uncover how these variables contribute to variations in the outcome under study. Initially, we conducted separate analysis for each intersection on the demographic factors, we made initial observant for each factor alone. Concluding how demographic factors to discern their individual influence on suicide rates . This provides understanding into how age and sex intersect to shape suicide risks. Subsequently, we explored intersections within the demographic factors to identify any changes in variation.

>>>>

This paper presents a comprehensive statistical model of the relationship between demographic factors - age, sex, and race - and their impact on suicide rates. Our objective is to uncover how these variables contribute to variations in the outcome under study. Initially, we conducted separate analysis for each intersection on the demographic factors, we made initial observant for each factor alone. Concluding how demographic factors to discern their individual influence on suicide rates . This provides understanding into how age and sex intersect to shape suicide risks. Subsequently, we explored intersections within the demographic factors to identify any changes in variation. All estimations were done through modelling that can be found in the file path scripts/04-model.R using the model summary of each respective findings.
